% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% start a document with the here given default font size and paper size
\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,margin=0.75in]{geometry}

\usepackage[english]{babel}
\hyphenation{Some-long-word}

\usepackage{resume}


\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins

\maintitle{Marcus McCurdy}{}% title on top of the document

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:marcus.mccurdy@gmail.com}
{marcus.mccurdy\mbox{}@\mbox{}gmail.com}\sbull
\href{http://github.com/volker48}{github.com/volker48} \sbull
\href{http://www.linkedin.com/in/marcusmccurdy}
    {www.linkedin.com/in/marcusmccurdy}
\\
224 Virginia Ave\sbull
Haddon Township, NJ 08108\sbull \textsmaller{+1}714-791-8345

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Engineer at heart who has always loved 
seeing the joy building something useful can bring to
others.}
\\

I'm a passionate and pragmatic programmer who believes done is better than 
perfect while at the same time believing that software shouldn't be rushed. 
I enjoy writing correct code while maintaining a sense of urgency and momentum. 
I use testing to provide myself with a tight feedback loop and the freedom to 
refactor without fear. I thrive working in an environment where I can  
collaborate with other developers on different aspects of our project resulting
in a cohesive business feature that brings value to the company.

\end{multicols}


\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection
  {\href{https://beaxy.com/}{Beaxy Digital Ltd.}}
  {\textsc{Remote} } 
  {%
   \headedsubsection
  {Data Scientist}
  {Dec\apo17 -- Present}
  {\bodytext{
      \begin{itemize}
          \item Work directly with CEO and CTO to code blockchain proof of concept applications.
          \item Architect scalable solutions to real time exchange transactions using NoSQL.
          \item Research cryptocurrency code bases in consideration of addition as trading pairs on the exchange.
      \end{itemize}
    }
  }
  }


\headedsection
  {\href{http://www.red-spark.com/}{Red Spark}}
  {\textsc{Philadelphia, Pennsylvania} } 
  {%
   \headedsubsection
  {Lead Data Scientist}
  {Feb\apo16 -- Present}
  {\bodytext{
      \begin{itemize}
          \item Brought over a dozen different models into production.
          \item Built a bid prediction model and increased profit on primary product by ~25\%. 
          \item Managed two other data scientist direct reports.
          \item Retreived, cleaned, and merged data from MySQL and User Voice and used the data for agglomerative
          clustering using scikit-learn.
          Analyzed 10 clusters for business importance and found a small cluster of customers generating the majority of profit.
          \item Implemented XGBoost model loading and inference in pure Go for use in a near real time prediction
          service making over 150k predictions per second with a round trip p95 latency of ~1.5 ms.
          \item Used PySpark to select, clean, transform, and extract terabytes of click stream data for usage in ML
          models.
          \item Created a keyword suggestion API using approximate nearest neighbors (ANNOY) and a Sanic webserver exposing a REST 
          prediction API.
          \item Developed a Docker container for the data science team to standardize our environments.
          \item Took an existing, unvalidated Vowpal Wabbit (VW) machine learning model and through feature engineering and
                hyperparameter tuning reduced Mean Squared Error from over 200 to less than 0.3.
          \item Developed, tested, and deployed a Vowpal Wabbit automatic model trainer. Pulls data from S3, trains
                VW, uploads model to production.
          \item Evaluated multiple machine learning models for revenue prediction testing models from Scikit-Learn
                and others including XGBoost, LightGBM, and SparkML.
      \end{itemize}

    }
  }
  
  \headedsubsection
  {Software Engineer Manager}
  {Sept\apo12 -- Feb\apo16}
  {\bodytext{
      \begin{itemize}
          \item Developed an ETL system in Go that streams data from S3, parses it, uploads back into S3, then performs a
                distributed RedShift load of the data.
          \item Developed a logging platform using OpenResty, LuaJIT, logrotate, and S3.
          \item Full stack development in Laravel developing 50's publisher dashboard.
          \item Lead developer on 50onRed's cross-browser JavaScript extension
              platform. A Python Flask web app backed by a {MySQL} database and {SQLAlchemy} {ORM}. The
              Flask app is served by uWSGI and reverse proxied by NGINX.
          \item Worked closely with operational analysts to provide custom
              reporting on 50's internal {PHP} dashboard and {MySQL} database.
          \item Updated a manual process of editing JavaScript in text fields
              and transformed it into a single page {AngularJS} application 
              providing a simple interface for creating ad units that are 
              compiled into fully functioning JavaScript ad units.
          \item Revolutionised 50's Python web scraping framework by rewriting
              a synchronous process into an asynchronous job queue with 
              \href{http://python-rq.org/}{RQ}.
          \item Major contributor to a Java and Jetty based popup serving
              daemon processing billions of requests daily.
          \item Implemented a concurrent Java application to process and 
              aggregate terabytes of {Akamai} log files daily and store them
              in a {PostgreSQL} database.
          \item Extensive {Amazon} {AWS} deployments and provisioning with
              {Ansible}.
          \item Installed and maintained a Sentry event logging 
              server to track errors across Java, Python, PHP, and 
              JavaScript code bases.
      \end{itemize}

    }
  }
  }

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://www.drexel.edu/}{Drexel University}}
  {\textsc{Philadelphia, Pennsylvania}} {%

  \headedsubsection  % sets the header for a subsection and contains usually body text
    {Research Engineer}
    {Apr\apo09 -- Sept\apo12}
    {\bodytext{
    \begin{itemize}
        \item Performed background research and drafted a proposal for an 
            internal R\&D online learning project focusing on integrating 
            artificial intelligence into Drexel's online courses. Proposal after
            research was approximately \$700,000 under initial estimates and 
            was presented to the president of the university.
        \item Technical lead on a US Army funded Android development project. 
            Assessing the feasibility of and implementing agent based networking
            applications. Also created scenarios for testing and evaluation of
            networking protocols and performed the evaluations.
        \item Team lead in the design and implementation of a 
    distributed collaborative battle command planning system for the US army. 
    Oversaw and mentored junior developers during the project while working
    closely with the lead system integrator to deliver a premium product. 
    Integrated the final product with systems from French and German allies. 
    Extensive use of Swing and {NASA}'s {World Wind}.
\item Designed and implemented an {HTTP} proxy in {C\#} for a biometrics 
    fingerprint scanner and webserver. The proxy was for both the client
    application of the fingerprint scanner and the webserver for matching and
    enrolling biometrics data. The proxy enables the client and server to
    use an in house pure C content based networking middleware.
    \end{itemize}
}}
 }


%\begin{center}
%  \emph{Please refer to \href{http://www.linkedin.com/in/marcusmccurdy}{my Linkedin profile} for the complete list of work experiences.}
%\end{center}


\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {Drexel University}
  {\textsc{Philadelphia, Pennsylvania}} {%
  \headedsubsection
    {Masters degree in Computer Science}
    {2009 -- 2012}
    {\bodytext{Focused on Artificial Intelligence.}}
}

\headedsection
  {California State University at Long Beach}
  {\textsc{Long Beach, California}} {%
  \headedsubsection
    {Bachelors degree in Computer Engineering}
    {2001 -- 2007} 
    {\bodytext{Minor in Computer Science.}}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical specialties:}
  {I have a passion for programming and often program just for fun. I've written the
  most production code in Python, {Go}, Java, PHP, and JavaScript. I'm obsessed with Machine Learning.
  I regularly enter ML contests on Kaggle and have success on NumerAI. While Python is currently my primary 
  day to day language I try to remain language agnostic and thoroughly enjoy learning new
  languages and I've dabbled in {Haskell}, {Clojure}, and {Ruby}. I've been using {Go} in production for performance critical and concurrent
  applications. I've also worked with both C and C++ including embedded programming in C on the 8051 microcontroller. Experience with web 
  technologies {HTML}, {CSS}, and {LESS}. Written the most {SQL} for both {MySQL} and {PostgreSQL} and
  deployed both databases to {AWS} and {DigitalOcean}. Linux system
  administration (mostly Ubuntu) on {AWS} and my own personal machine. 
  I use {Git} and Mercurial daily. I currently use IntelliJ as my IDE, but have used Visual 
  Studio for {C\#} and {C++} development. My editor of choice is Vim despite 
  attempts to coerce me into using Emacs.}

\inlineheadsection
  {Natural languages:}
  {English \emph{(native), German \emph{(limited)}.}}


\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {Biking, cooking, cryptographic currencies, CrossFit, gaming, hiking, 
  Olympic lifting, programming, reading, and running.}


\end{document}
